---
title: "p8105_hw1_hh3043"
author: "Haitian Huang"
date: "2023-09-22"
output: html_document
---
# Problem 1


```{r echo = FALSE}
library('moderndive')
library(ggplot2)
data('early_january_weather')

```

This dataset formed by weather data collected in January 2013 for LGA, JFK and EWR .

There are 15 variables:origin,year,month,day,hour,
temperature,dewpoint in F,humid,wind direction,wind speed,
gust speed,precipitation,pressure,visibility and data and hour of recording as POSIXct date.

There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean of temperatures is `r colMeans(early_january_weather[,6])`.



```{r echo = FALSE}

ggplot(early_january_weather,aes(time_hour,temp,color = humid))+geom_point()
```

From the graph, we can see in general temperature is positively proportional to time_hour. When time_hour and temp are high,humid is high.


# problem 2

```{r}
library(tidyverse)
df = 
  tibble(
  vec_num = rnorm(10),
  vec_log = vec_num>0,
  vec_character = sample(c('w','e'),size=10,replace = TRUE),
  vec_factor = factor(c(sample(c('dog','cat','mouse'),size=10,replace = TRUE)))
)
