---
title: "p8105_hw1_hh3043"
author: "Haitian Huang"
date: "2023-09-22"
output: html_document
---
# Problem 1


```{r echo = FALSE}
library('moderndive')
library(ggplot2)
data('early_january_weather')

```

This dataset formed by weather data collected in January 2013 for LGA, JFK and EWR .

There are 15 variables:origin,year,month,day,hour,
temperature,dewpoint in F,humid,wind direction,wind speed,
gust speed,precipitation,pressure,visibility and data and hour of recording as POSIXct date.

There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean of temperatures is `r colMeans(early_january_weather[,6])`.



```{r echo = FALSE}

ggplot(early_january_weather,aes(time_hour,temp,color = humid))+geom_point()
```

From the graph, we can see in general temperature is positively proportional to time_hour. When time_hour and temp are high,humid is high.


# problem 2

```{r}
library(tidyverse)
df = 
  tibble(
  vec_num = rnorm(10),
  vec_log = vec_num>0,
  vec_character = sample(c('w','e'),size=10,replace = TRUE),
  vec_factor = factor(c(sample(c('dog','cat','mouse'),size=10,replace = TRUE)))
)
```


```{r eval = FALSE}
mean(pull(df,vec_num))
mean(pull(df,vec_log))
mean(pull(df,vec_character))
mean(pull(df,vec_factor))
```
The mean() method works for random sample and logic vector,but NA is returned for 
vector of character and vector of factor.The mean of random sample is `r mean(pull(df,vec_num))`,and the mean of logic vector is `r mean(pull(df,vec_log))`.

```{r eval = FALSE}
as.numeric(pull(df,vec_num))
as.numeric(pull(df,vec_log))
as.numeric(pull(df,vec_character))
as.numeric(pull(df,vec_factor))
```
The as.numeric method works for random sample,logic vector and vector of factor,returning NA for vector of character.Of course it works for random sample,because random sample is already in numeric form.

Through as.numeric,TRUE is transferred to 1,and FALSE is transferred to 0.There exists statistical significance with mean() method.By taking the mean of these 0 and 1,we can get the ratio of number of TRUE to number of FALSE.

As for vector of factor,there is no clear statistical significance of mean,since numbers are transferred according to the order of levels.It might be the reason why mean() does not work on it.

For vector of factor,it can not be transferred to numeric even through as.numeric() method.That's why mean() method doesn't work.

